---
title: "1. Pre-processing data"
output: 
  html_notebook: 
    fig_width: 8
    toc: yes
    code_folding: show
author: "David Innes"
editor_options: 
  chunk_output_type: inline
---

This whole analysis requires a data frame with only the following columns:

1. `Cow` - cow's number identification
2. `Parity` - number representing what parity the lactation represents
3. `ID` -  lactation ID in the format: Cow_Parity (This can be added here using `mutate()` and `str_c()`)
4. `DIM` - days in milk; d
5. `my` - milk yield; kg


Step 1 (in this file) has 3 main steps:

1. clean data - described in function: `f_clean_lac_data.R`
2. describe data - `f_descriptive_stats.R`
3. summarise lactation data - `f_summary_tables.R`


```{r setup, echo=TRUE, results='hide'}
suppressPackageStartupMessages(library(tidyverse))
library(slider)

# load required functions:
source("./functions/f_clean_lac_data.R")
source("./functions/f_descriptive_stats.R")
source("./functions/f_summary_tables.R")

```

# Import
```{r echo=TRUE, results='hide'}
# Import file
workingfile <- data.table::fread("./Inputs/simulated_exlac_data.csv") %>% 
  #rename column to match requirements of scripts:
  rename(Cow = cow_ID)

glimpse(workingfile) 

```

# a) Data cleaning

## Execute cleaning steps
```{r echo=TRUE, results='hide'}
# generate_plots = FALSE prevents individual lactation plots from being generated.
list_output <- f_clean_lac_data(workingfile, generate_plots = TRUE)
```

## Print log
Because this is a synthetic dataset, many errors are not detected here. 
```{r}
list_output$log$Step1_NA_removed

list_output$log[-1]

```

## Diagnostic Plots
```{r}
list_output$plots$n_per_DIM_prefilter

list_output$plots$n_per_DIM_postfilter
```

### Plot of lactations removed with break mid-lac

```{r}
list_output$plots$lacs_mid_break_REMOVED
```


## Example of output plots
```{r eval=FALSE}
# Only works if generate_plots = TRUE
list_output$plots$list_gap_classification_plots$`1035_2`

list_output$plots$list_outlier_detection_plots$`1705_3`
```

## Save plots
This can take a while, and is better executed on a larger computer.
```{r eval=FALSE, include=TRUE}
# Only works if generate_plots = TRUE


f_plot <- function(.x, .y){
  plot_in <- .x
  name_in <- .y
  
  p <- ggsave(filename = paste0("outlier_plot_",name_in,".png"),
               path = "./Plots/Outlier_Detection/", 
              #path = "./R_lac/Plots/Gap_Detection/",
                plot =  plot_in,
                dpi = 150,
                width=10,
               height=7)
  }
  
list_to_plot <- list_output$plots$list_outlier_detection_plots[1:3]
#list_to_plot <- list_output$plots$list_gap_classification_plots[1:3]

map2(.x = list_to_plot, .y = names(list_to_plot), .f = f_plot )



```


## OUTPUT total_MY_summary
This is required for downstream analysis, so save here.
Saving files as .rds is much quicker and preserves some formatting.

```{r}
# Save cleaned_data. 
saveRDS(list_output$cleaned_data, "./Outputs/cleaned_data_out.rds")

data.table::fwrite(list_output$total_MY_summary, "./Outputs/total_MY_summary_out.csv")
saveRDS(list_output$total_MY_summary, "./Outputs/total_MY_summary_out.rds")

```



# b) Summary Descriptive Stats
This function summarises the data to match output for Table 1 in publication. 

```{r}
(df_descriptive_stats_FULL <- 
  f_descriptive_stats(cleaned_data_in = list_output$cleaned_data)
 )
```



# c) Summarise characteristics of lactation
This data is calculated to write in-text, not in a table.
## by Parity
```{r}
(parity_summary <- f_summary_tables(list_output$cleaned_data, 
                   list_output$total_MY_summary,
                   to_group_by = Parity_class))

# view only means
#parity_summary %>% filter(str_detect(name, 'mean'))

```

## by Lactation length
```{r}

(lac_len_summary <- f_summary_tables(list_output$cleaned_data, 
                   list_output$total_MY_summary,
                   to_group_by = Lac_len_group))


#lac_len_summary %>% filter(str_detect(name, 'mean'))

```


# OUTPUT tables to excel
Save an excel file with different outputs in each sheet to the `Outputs/` folder.
```{r}
# add to named list. Names = sheet names in excel output
tables_out_list <- 
  list(df_descriptive_stats_FULL = df_descriptive_stats_FULL,
     parity_summary = parity_summary,
     lac_len_summary = lac_len_summary
     )

# adds a timestamp to filename:
openxlsx::write.xlsx(tables_out_list,
                     file = paste0("./Outputs/lac_summary_tables ",
                                   format(Sys.time(), "%Y%m%d_%H%M") ,
                                   ".xlsx"),
                     colWidths = "auto")
# 
```

