---
title: "Post-fitting tables and plots"
author: "David Innes"
output: 
  html_notebook: 
    fig_width: 10
    toc: yes
    code_folding: show
editor_options: 
  chunk_output_type: inline
---

This runs through generating:

a) Summary tables
b) Plots
c) t-tests

All from the output of the fitting of the 3 lactation models. 


```{r setup, echo=FALSE, warning=FALSE, message=FALSE}

suppressPackageStartupMessages(library(tidyverse, warn.conflicts = FALSE))
library(patchwork)
# requires: rstatix

source("./functions/f_fitted_summary_tables.R")
source("./functions/f_plot_mean_lac_curves.R")
source("./functions/f_plot_individual_three_models.R")
source("./functions/f_t_test_output.R")

```


# Import
Uses the file exported by the ['2.fit_3_lac_models_parallel.R'](2.fit_3_lac_models_parallel.R) run on server.

```{r echo=FALSE}
# Import files. It's also stored as a .csv but using .rds is faster.
# also ungroup all df to avoid unpredictable behaviour.

combined_fit_stats <- 
  readRDS("./Outputs/combined_fit_stats.rds") %>% 
  ungroup() %>% 
  #reorder to match desired output
  mutate(Parity_class = factor(Parity_class, levels = c("Primiparous", "Multiparous")),
         Model = factor(Model, levels = c('Wood', 'Wilmink','Dijkstra')))

combined_params <- 
  readRDS("./Outputs/combined_params.rds") %>% 
  ungroup() %>% 
  #reorder to match desired output
  mutate(Parity_class = factor(Parity_class, levels = c("Primiparous", "Multiparous")),
         Model = factor(Model, levels = c('Wood', 'Wilmink','Dijkstra')))

combined_preds_fitted <- 
  readRDS("./Outputs/combined_preds_fitted.rds") %>% 
  ungroup() 

# for t-tests
cleaned_data <- readRDS("./Outputs/cleaned_data_out.rds") %>% ungroup()


```

# a) Summary tables
## Parity
### calculate summary tables
```{r message=FALSE}
Parity_params_summary_raw <- 
  combined_params %>% 
    f_fitted_summary_tables(groups_by = c(Model, Parity_class))
```

```{r}
Parity_params_summary_formatted <- 
  f_format_pub(Parity_params_summary_raw, groups_by = c(Model, Parity_class)) 

Parity_params_summary_formatted 
```


### Fit stats summary
```{r message=FALSE}
# summarise mean and SD
parity_fit_stats <- 
  combined_fit_stats %>% 
  f_fit_stats_summary(groups_by = c(Model, Parity_class))

# summarise output for table in paper
parity_fit_stats_formatted <-
  parity_fit_stats %>% 
  select(Model, Parity_class, starts_with(c("R2","MAE", "RMSPE", "RMSE", "CCC", "r_","Cb", "DW"))) %>% 
  mutate(across(where(is.double), ~round(.x,2)  )) %>% 
  f_format_pub(groups_by=c(Model, Parity_class))



parity_fit_stats_formatted
```



## Lactation length
### Summary
```{r message=FALSE}
laclen_params_raw <- 
  f_fitted_summary_tables(combined_params, groups_by = c(Model, Lac_len_group))

```


### Formatted for publication
```{r}
laclen_params_formatted <-
  f_format_pub(laclen_params_raw, c(Model,Lac_len_group))

laclen_params_formatted
```


### Fit stats summary
```{r message=FALSE}
# summarise mean and SD
laclen_fit_stats <- 
  combined_fit_stats %>% 
  f_fit_stats_summary(groups_by = c(Model, Lac_len_group))

# summarise output for table in paper
laclen_fit_stats_formatted <-
  laclen_fit_stats %>% 
  select(Model, Lac_len_group, starts_with(c("R2","MAE", "RMSPE","RMSE","CCC", "r_","Cb", "DW"))) %>% 
  mutate(across(where(is.double), ~round(.x,2)  )) %>% 
  f_format_pub(groups_by=c(Model, Lac_len_group))


laclen_fit_stats_formatted
```


## Output Tables
```{r}
# add to named list. Names = sheet names in excel output
tables_out_list <- 
  list(
    Parity_params_raw = Parity_params_summary_raw,
    Parity_params_formatted = Parity_params_summary_formatted ,
    Parity_fit_stats_raw = parity_fit_stats,
    Parity_fit_stats_formatted = parity_fit_stats_formatted,
    LacLen_params_raw = laclen_params_raw,
    LacLen_params_formatted = laclen_params_formatted,
    LacLen_fit_stats_raw = laclen_fit_stats,
    LacLen_fit_stats_formatted = laclen_fit_stats_formatted
     )

# export
openxlsx::write.xlsx(tables_out_list,
                     file = paste0("./Outputs/model_summary_tables ",
                                   format(Sys.time(), "%Y%m%d_%H%M") ,
                                   ".xlsx"),
                     colWidths = "auto")
```


# b) Plots
## Grouped plots
### by Parity
```{r}
f_plot_mean_lac_curves(combined_preds_fitted_in = combined_preds_fitted,
                       groups_by = Parity_class,
                      plot_n_colour = "log2")
```

### by Lactation length
```{r fig.width = 7}
f_plot_mean_lac_curves(combined_preds_fitted_in = combined_preds_fitted,
                       groups_by = Lac_len_group,
                      plot_n_colour = "log2")


```


## Residual summary plots

```{r}
(p_resid_parity <- 
  f_plot_mean_lac_curves(combined_preds_fitted_in = combined_preds_fitted,
                       groups_by = Parity_class,
                      plot_residuals = TRUE)+
  labs(title = "a)")
)
```

```{r message=FALSE}
(p_resid_lacgroup <- 
  f_plot_mean_lac_curves(combined_preds_fitted_in = combined_preds_fitted,
                       groups_by = Lac_len_group,
                      plot_residuals = TRUE)+
  labs(title = "b)")
)
```


## combined residual plots for publication
```{r message=FALSE, fig.height = 8, fig.width = 6}
# plot one of top of each other
(p_resid_combined_publish <- p_resid_parity / p_resid_lacgroup)

```

Save plots in .png for word and .tiff for high resolution:
```{r eval=FALSE}
# .png
ggsave(filename = paste0("residual_points_combined_", 
                         format(Sys.time(), "%Y%m%d_%H%M") ,
                         ".png"),
              path = "./Outputs/",
              plot = p_resid_combined_publish,
              dpi = 600,
              width=9,
              height=10)

# .tiff  - high resolution
ggsave(filename = paste0("residual_points_combined_", 
                         format(Sys.time(), "%Y%m%d_%H%M") ,
                         ".tiff"),
              path = "./Outputs/",
              plot = p_resid_combined_publish,
              dpi = 600,
              width=9,
              height=10)
```



## Observed with error
plot observed points with error bars

```{r message=FALSE}
observed_means <- 
  combined_preds_fitted %>% 
  filter(Model == "Dijkstra") %>% 
  group_by(Parity_class, Model, DIM) %>%
  mutate(Parity_class = factor(Parity_class, levels = c("Primiparous", "Multiparous"))) %>% 
  summarise(mean_observed_my = mean(my, na.rm=TRUE),
            mean_observed_SD = sd(my, na.rm=TRUE),
            n = n(),
            mean_osbserved_SEM = mean_observed_SD/sqrt(n))

p_observed_summary <- observed_means %>% 
  ggplot()+
  geom_smooth(aes(x=DIM, y = mean_observed_my - mean_osbserved_SEM), color = 'grey10', linewidth = 0.8, span = 0.05, se=FALSE)+
  geom_smooth(aes(x=DIM, y = mean_observed_my + mean_osbserved_SEM), color = 'grey10', linewidth = 0.8, span = 0.05, se=FALSE)+
  geom_point(aes(x=DIM, y = mean_observed_my, colour = n), alpha=0.3, size = 2)+
  viridis::scale_color_viridis(direction = -1, option = "H", trans = "log2", labels = ~round(.,0), begin = 0.1)+
  facet_wrap(facets="Parity_class", ncol = 1)+
  scale_x_continuous(n.breaks = 10)+
  ggpubr::theme_classic2()+
  xlab("Days in milk (DIM)")+
  ylab("Milk Yield (kg/d)")
  
p_observed_summary
  
```

Save:
```{r eval=FALSE}
# .png
ggsave(filename = paste0("p_observed_summary ", 
                         format(Sys.time(), "%Y%m%d_%H%M") ,
                         ".png"),
              path = "./Outputs/",
              plot = p_observed_summary,
              dpi = 600,
              width=9,
              height=7)


# .tiff
ggsave(filename = paste0("p_observed_summary ", 
                         format(Sys.time(), "%Y%m%d_%H%M") ,
                         ".tiff"),
              path = "./Outputs/",
              plot = p_observed_summary,
              dpi = 600,
              width=9,
              height=7)
```


## Individual plot examples


### Get worst and best fits
Ranked on mean of MAE (%) across 3 fits.
```{r}
worst_fits <- 
  combined_fit_stats %>% 
  group_by(ID) %>% 
  summarise(mean_MAE = mean(MAE_perc, na.rm=TRUE)) %>%  
  slice_max(order_by = mean_MAE, n = 6) %>% 
  arrange(desc(mean_MAE))

worst_fits_ID <- worst_fits %>% pull(ID) %>% unique()


best_fits <-
  combined_fit_stats %>% 
  group_by(ID) %>% 
  summarise(mean_MAE = mean(MAE_perc, na.rm=TRUE)) %>%  
  slice_min(order_by = mean_MAE, n = 6) %>% 
  arrange(mean_MAE)

best_fits_ID <- best_fits %>% pull(ID) %>% unique()
```


#### 6 best fits 
```{r fig.width = 10, message=FALSE}
p_best_fits_a <- 
  f_plot_individual_three_models_2_errors(
  combined_fit_stats,
  combined_preds_fitted,
  error_rank = "MAE",
  best_fits_ID, 
  y_label_loc = 4,
  ymax = 80,
  "a)")+ coord_cartesian(ylim = c(-5, NA))

p_best_fits_a

```


#### 6 worst fits
```{r fig.width = 10, message = FALSE}

p_worst_fits_b <- 
  f_plot_individual_three_models_2_errors(
  combined_fit_stats, 
  combined_preds_fitted,
  error_rank = "MAE",
  worst_fits_ID, 
  y_label_loc = 40,
  ymax = 60,
  plot_title = "b)")+ coord_cartesian(ylim = c(-5, NA))

p_worst_fits_b 
                     
```


### combined best/worst plots for publication
```{r message=FALSE}
p_best_worst_publish <- p_best_fits_a / p_worst_fits_b
```

save:
```{r eval=FALSE}
#.png
ggsave(filename = paste0("p_ind_fits_best_worst_combined ", 
                         format(Sys.time(), "%Y%m%d_%H%M") ,
                         ".png"),
              path = "./Outputs/",
              plot = p_best_worst_publish,
              dpi = 600,
              width=10,
              height=12)

# .tiff
ggsave(filename = paste0("p_ind_fits_best_worst_combined ", 
                         format(Sys.time(), "%Y%m%d_%H%M") ,
                         ".tiff"),
              path = "./Outputs/",
              plot = p_best_worst_publish,
              dpi = 600,
              width=10,
              height=12)
```


# c) t-tests
Run t test comparisons between mean values.
Comparisons between parity or lactation length, within each model.
Output tables to 1 excel file.

## Format data for downstream
```{r}
# convert to long format, set some cols as factors

# Parameters:
combined_params_long <-  
  combined_params %>% 
  ungroup() %>% 
  mutate(Parity_class = factor(Parity_class, levels = c("Primiparous", "Multiparous")),
         Model = factor(Model, levels = c('Wood', 'Wilmink','Dijkstra'))) %>% 
  rename_at(vars(contains("Mp")), list(~str_replace(., "Mp", "Peak_Yield_kg"))) %>% 
  rename_at(vars(contains("Tp")), list(~str_replace(., "Tp", "Time_to_PY_d"))) %>% 
  select(-contains('maxDIM'), -contains('tmax'), -contains('t_max')) %>% 
  select(ID, Parity_class, Model, Lac_len_group, where(is.numeric)) %>% 
  pivot_longer(cols = where(is.double),
               values_to = 'value',
               names_to = 'variable')


# fit stats:
combined_fits_long <-  
  combined_fit_stats %>% 
  ungroup() %>% 
  mutate(Parity_class = factor(Parity_class, levels = c("Primiparous", "Multiparous")),
         Model = factor(Model, levels = c('Wood', 'Wilmink','Dijkstra'))) %>% 
  select(ID, Parity_class, Model, Lac_len_group, where(is.numeric)) %>% 
  pivot_longer(cols = where(is.double),
               values_to = 'value',
               names_to = 'variable')

```




## Parity comparison

### Model parameters
Iterate through groups for t test.
```{r}
# Run t test on all groups, using nesting as we are comparing Parity WITHIN Model.
model_parity_t_test_out <- 
 combined_params_long %>% 
  f_t_test_output(group_by = 'Parity_class')


model_parity_t_test_out
```

### letter comparisons
This prints letters to help interpretation
```{r}
# format to get letters in similar format to means.
model_parity_letters <- 
  model_parity_t_test_out %>% 
  mutate(primiparous = case_when(sig == TRUE ~ "a", TRUE ~ "NS"),
         multiparous = case_when(sig == TRUE ~ "b", TRUE ~ "NS")) %>% 
  select(Model, variable, primiparous, multiparous)  %>% 
    pivot_longer(cols = primiparous:multiparous) %>% 
    pivot_wider(names_from = c(Model, name),
                names_sep = "_",
                values_from = value)

model_parity_letters

```


### Fit stats comparison
```{r}
# Run t test on all groups, using nesting as we are comparing Parity WITHIN Model.
fits_parity_t_test_out <- 
  combined_fits_long %>% 
  f_t_test_output(group_by = 'Parity_class')


fits_parity_t_test_out

```

### letter comparisons
This prints letters to help interpretation
```{r}
# format to get letters in similar format to means.
stats_parity_letters <- 
  fits_parity_t_test_out %>% 
  mutate(primiparous = case_when(sig == TRUE ~ "a", TRUE ~ "NS"),
         multiparous = case_when(sig == TRUE ~ "b", TRUE ~ "NS")) %>% 
  select(Model, variable, primiparous, multiparous)  %>% 
    pivot_longer(cols = primiparous:multiparous) %>% 
    pivot_wider(names_from = c(Model, name),
                names_sep = "_",
                values_from = value)

stats_parity_letters

```

## Lactation length comparison

### Model parameters
```{r}

model_lac_group_t_test <- 
  combined_params_long %>% 
  f_t_test_output(group_by = 'Lac_len_group')


model_lac_group_t_test
```

### letter comparisons
```{r}
# format to get letters in similar format to means.
model_lac_group_letters <- 
  model_lac_group_t_test %>% 
  mutate(group1 = case_when(sig == TRUE ~ "a", TRUE ~ "NS"),
         group2 = case_when(sig == TRUE ~ "b", TRUE ~ "NS")) %>% 
  select(Model, variable, group1, group2) %>% 
    pivot_longer(cols = group1:group2) %>% 
    pivot_wider(names_from = c(Model, name),
                names_sep = "_",
                values_from = value)

model_lac_group_letters

```


### Fit stats comparison

```{r}

fits_groups_t_test_out <- 
  combined_fits_long %>% 
 f_t_test_output(group_by = 'Lac_len_group')


fits_groups_t_test_out
```



### letters
```{r}
# format to get letters in similar format to means.
fits_lac_group_letters <- 
  fits_groups_t_test_out %>% 
  mutate(group1 = case_when(sig == TRUE ~ "a", TRUE ~ "NS"),
         group2 = case_when(sig == TRUE ~ "b", TRUE ~ "NS")) %>% 
  select(Model, variable, group1, group2) %>% 
    pivot_longer(cols = group1:group2) %>% 
    pivot_wider(names_from = c(Model, name),
                names_sep = "_",
                values_from = value)

fits_lac_group_letters

```



# Output Tables
```{r}
# add to named list. Names = sheet names in excel output
tables_out_list <- 
  list(
    parity_params_t_test= model_parity_t_test_out,
    parity_params_letters = model_parity_letters,
    parity_stats_t_test = fits_parity_t_test_out,
    parity_stats_letters = stats_parity_letters,
    lac_len_params_t_test = model_lac_group_t_test,
    lac_len_params_letters = model_lac_group_letters,
    lac_len_stats_t_test = fits_groups_t_test_out,
    lac_len_stats_lettesr = fits_lac_group_letters
     )


# export
openxlsx::write.xlsx(tables_out_list,
                     file = paste0("./Outputs/t_test_tables ",
                                   format(Sys.time(), "%Y%m%d_%H%M") ,
                                   ".xlsx"),
                     colWidths = "auto")

```


