---
title: "4a. Prepare data for iterative fitting"
author: 'David Innes'
output: 
  html_notebook: 
    toc: yes
    code_folding: show
editor_options: 
  chunk_output_type: inline
--- 


Prepare data by removing lactations that did not converge with full dataset.

```{r setup, echo=TRUE, results='hide'}
library(tidyverse)
library(patchwork)

source("./functions/f_descriptive_stats.R")
```

# Import data
```{r}
cleaned_data <- 
  readRDS("./Outputs/cleaned_data_out.rds") %>% 
  ungroup() %>% 
  select(Cow, Parity, ID, DIM, my, maxDIM)


combined_fit_info <- readRDS("./Outputs/combined_fit_info.rds")

combined_fit_stats <- readRDS("./Outputs/combined_fit_stats.rds") %>%  ungroup() 

combined_params <-  readRDS("./Outputs/combined_params.rds") %>% ungroup() 

```

## Remove non-converged 
Re-calculates the descriptive stats for this dataset
```{r}
# remove non-converged and only Dijkstra model
converged_IDs <- 
  combined_fit_info  %>% 
  filter(Model == "Dijkstra", isConv) %>% 
  pull(ID)

working_data <- 
  cleaned_data %>% 
  filter(ID %in% converged_IDs)


new_descriptive_stats <- 
  f_descriptive_stats(cleaned_data_in = working_data) 

#print(paste("Dimensions converged-only dataset: ", dim(working_data)))
new_descriptive_stats
```


# Output descriptive stats table
```{r eval=FALSE}
data.table::fwrite(new_descriptive_stats, 
                   file = paste0("./Outputs/iterated_descritive_stats_filtered_data ",
                                 format(Sys.time(), "%Y%m%d_%H%M"),
                                 ".csv"))
```

# Export filtered data
```{r eval=FALSE}
saveRDS(working_data, paste0("./Outputs/filtered_cleaned_data",
                             format(Sys.time(), "%Y%m%d_%H%M"),
                             ".rds"))
```


# Calculate SD of b, b0 and c parameter
To set bounds on the c parameter for the sectional fits we need to use the previous fit data.
This is only to define 'biologically meaningful' numbers and doesn't necessarily rely on a full analysis prior.

show means of all (converged and non-converged):
```{r}
combined_params_conv <- 
combined_fit_info %>% 
  filter(Model == "Dijkstra") %>% 
  select(ID, isConv) %>% 
  left_join(
    combined_params %>% 
      filter(Model == "Dijkstra") 
  ) 

 
combined_params_conv %>% 
  summarise(across(c(b,b0,c), list(mean = mean, sd = sd), .names = "{.col}_{.fn}")) 

  
```

Show means of just converged == TRUE. 
```{r}
param_bounds <- 
combined_params_conv %>% 
  group_by(isConv) %>% 
  summarise(across(c(b,b0,c), list(mean = mean, sd = sd), .names = "{.col}_{.fn}")) %>% 
  filter(isConv == TRUE) 
param_bounds

```


## b Param
### Plot
```{r}
mean_b <- pull(param_bounds, b_mean)
sd_b <- pull(param_bounds, b_sd)

(p_b <- 
combined_params_conv %>% 
  ggplot(aes(x = b, fill = isConv))+
  geom_histogram(binwidth = 0.01)+
  scale_fill_viridis_d(option = "D", begin = 0.15, end = 0.85)+
  scale_x_continuous(n.breaks = 10)+
  geom_vline(aes(xintercept=mean_b), colour = 'black')+
  geom_vline(aes(xintercept=mean_b + sd_b), colour = 'black', linetype = 'dashed' )+
  geom_vline(aes(xintercept=mean_b - sd_b), colour = 'black', linetype = 'dashed' )+
  labs( 
    title = "a)",
    fill = "Converged?",
    )+
  ggpubr::theme_classic2() +
  NULL
)
```


## b0 Param
### Plot
```{r}
mean_b0 <- pull(param_bounds, b0_mean)
sd_b0 <- pull(param_bounds, b0_sd)

(
p_b0 <- 
combined_params_conv %>% 
  ggplot(aes(x = b0,fill = isConv))+
  geom_histogram(binwidth = 0.01)+
  scale_fill_viridis_d(option = "D", begin = 0.15, end = 0.85)+
  scale_x_continuous(n.breaks = 10)+
  geom_vline(aes(xintercept=mean_b0), colour = 'black')+
  geom_vline(aes(xintercept=mean_b0 + sd_b0), colour = 'black', linetype = 'dashed' )+
  geom_vline(aes(xintercept=mean_b0 - sd_b0), colour = 'black', linetype = 'dashed' )+
  labs(
    title = "b)",
    fill = "Converged?",
    )+
  ggpubr::theme_classic2() +
  NULL
)

```




## c Param

### Plot
```{r}
mean_c <- pull(param_bounds, c_mean)
sd_c <- pull(param_bounds, c_sd)

p_c <- 
  combined_params_conv %>% 
  ggplot(aes(x = c,  fill = isConv))+
  geom_histogram(binwidth = 0.001)+
  scale_fill_viridis_d(option = "D", begin = 0.15, end = 0.85)+
  scale_x_continuous(n.breaks = 10)+
  scale_y_continuous(trans = 'pseudo_log')+
  labs(
    title = "c)",
    fill = "Converged?",
    y = 'count (log scale)',
    )+
  ggpubr::theme_classic2() +
  NULL

p_c 


```



### Refine c further
Visually, it looks like the large outliers are pulling the mean away from the actual 'normal curve' 
```{r}

new_c_bounds <- 
combined_params_conv %>% 
  filter(c <= 0.006) %>% # manually selected threshold
  group_by(isConv) %>% 
  summarise(across(c(c), list(mean = mean, sd = sd), .names = "{.col}_{.fn}")) %>% 
  filter(isConv == TRUE) 



mean_c <- pull(new_c_bounds, c_mean)
sd_c <- pull(new_c_bounds, c_sd)

p_c2 <- 
combined_params_conv %>% 
  filter(c < 0.02) %>% 
  ggplot(aes(x = c, fill = isConv))+
  geom_histogram(binwidth = 0.0001)+
    scale_fill_viridis_d(option = "D", begin = 0.15, end = 0.85)+
  scale_x_continuous(n.breaks = 10)+
  geom_vline(aes(xintercept=mean_c), colour = 'black')+
  geom_vline(aes(xintercept=mean_c + sd_c * 1.5), colour = 'black', linetype = 'dashed' )+
  geom_vline(aes(xintercept=mean_c - sd_c * 1.5), colour = 'black', linetype = 'dashed' )+
  
  geom_vline(aes(xintercept=0.006), colour = 'gold4', linetype=6, linewidth = 1)+
  labs(
    title = "d)",
    fill = "Converged?",
  )+
  ggpubr::theme_classic2() +
  NULL

p_c2

```

# Join plots

```{r fig.width = 10}
(p_combined_publish <- (p_b + p_b0) / (p_c + p_c2) )
```


```{r eval=FALSE}
# change to .tiff for high-resolution for publication
ggsave(filename = "combined_histograms_Dijkstra_params.png", 
       plot = p_combined_publish, 
       path = "./Outputs/",
       dpi = 600,
       width = 10,
       scale = 1.2)
```



## final bounds
The adjustments for 0 values is done automatically within `f_iterate_fitting.R`
```{r}
# b
lower_bound_b <- mean_b - (sd_b * 1)
upper_bound_b <-  mean_b + (sd_b * 1)
# lower_bound_b is lower than 0, which is impossible. Therefore, set as 0.
print("b param - lower bound: 0 (can't be neg; add 0e-08 as can't be actually 0 either)")
print(paste("b param - upper bound: ", round(upper_bound_b, 5)  ))


#b0
upper_bound_b0 <-  mean_b0 + (sd_b0 * 1)
lower_bound_b0 <- mean_b0 - (sd_b0 * 1)
print(paste("b0 param - lower bound: ", round(lower_bound_b0,5)))
print(paste("b0 param - upper bound: ", round(upper_bound_b0, 5)  ))

# c
upper_bound_c <-  mean_c + (sd_c * 1.5)
lower_bound_c <- mean_c - (sd_c * 1.5)


# lower_bound_c is lower than 0, which is impossible. Therefore, set as 0.
if(lower_bound_c > 0){
  print(paste("c param - lower bound: ", round(lower_bound_c, 5) ))
} else print("c param - lower bound: 0 (can't be neg; add 0e-08 as can't be actually 0 either)")

print(paste("c param - upper bound: ", round(upper_bound_c, 5)  ))
```








