---
title: "4b. Post-iteration analysis"
output: 
  html_notebook: 
    fig_width: 8
    toc: yes
    code_folding: show
author: "David Innes"
editor_options: 
  chunk_output_type: inline
---

This takes the output from Step 4 to make tables and plots. The input can therefore be 'constrained' or 'default/unconstrained', referring to if the parameters b, b0 and c were constrained within 'bounds' when fitting with nlis. All output is labelled based on flag (TRUE/FALSE) set at start.

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
suppressPackageStartupMessages(library(tidyverse, warn.conflicts = FALSE))
library(ggpp) #for geom_table()

source("./functions/f_lac_equations.R")
source("./functions/f_goodness_of_fit.R")
source("./functions/f_fitted_summary_tables.R")
```

```{r}
# SET FLAG FOR IF OUTPUT IS CONSTRAINED (T) OR DEFAULT (F):
is_constrained <- FALSE
```

# Import

## constrained:

```{r echo=FALSE}
if(is_constrained){
i_combined_fit_stats <- 
  readRDS("./Outputs/params_constrained_iterated_DIM_fit_stats.rds") %>% 
  ungroup() 

i_combined_params <- 
  readRDS("./Outputs/params_constrained_iterated_DIM_params.rds") %>% 
  ungroup() 

i_fitted_MY_all <- 
  readRDS("./Outputs/params_constrained_iterated_DIM_fitted_MY_all.rds") %>% 
  ungroup() 

i_fitted_305d_MY <- 
  readRDS("./Outputs/params_constrained_iterated_DIM_fitted_305d_MY.rds") %>% 
  ungroup()


i_combined_fit_info <- 
  readRDS("./Outputs/params_constrained_iterated_fit_info_.rds") %>% 
  ungroup()


i_combined_preds_out <- 
  readRDS("./Outputs/params_constrained_iterated_preds_out.rds") %>% 
  ungroup()


P_values_wide <- 
  readRDS("./Outputs/params_constrained_iterated_Pvalues_wide.rds") %>% 
  ungroup()


P_values_full <- 
  readRDS("./Outputs/params_constrained_iterated_Pvalues_FULL.rds") %>% 
  ungroup()
} 
```

## default:

```{r echo=FALSE}
if(is_constrained == FALSE){
i_combined_fit_stats <- 
  readRDS("./Outputs/params_default_iterated_DIM_fit_stats.rds") %>% 
  ungroup() 

i_combined_params <- 
  readRDS("./Outputs/params_default_iterated_DIM_params.rds") %>% 
  ungroup() 

i_fitted_MY_all <- 
  readRDS("./Outputs/params_default_iterated_DIM_fitted_MY_all.rds") %>% 
  ungroup() 

i_fitted_305d_MY <- 
  readRDS("./Outputs/params_default_iterated_DIM_fitted_305d_MY.rds") %>% 
  ungroup()


P_values_wide <- 
  readRDS("./Outputs/params_default_iterated_Pvalues_wide.rds") %>% 
  ungroup()


P_values_full <- 
  readRDS("./Outputs/params_default_iterated_Pvalues_FULL.rds") %>% 
  ungroup()
}
```


```{r}
# check n
i_combined_params %>% group_by(DIM_thresh) %>% count()
```

# Summarise params

All Inf values are set to Nan and therefore not included within summary stats

```{r message=FALSE}
summarised_params <- 
    i_combined_params %>% 
  f_fitted_summary_tables(groups_by=DIM_thresh)

summarised_params

```

## Format

```{r message=FALSE}

summarised_params_formatted <- 
  summarised_params %>% 
  mutate(DIM_thresh = factor(DIM_thresh, 
                             levels = as.character(c(30, 60, 90, 120, 150, 200, 250, 300)))) %>% 
  f_format_pub(groups_by = DIM_thresh) %>% 
  mutate(across(where(is.double),~signif(.x,3)))

summarised_params_formatted 
  

```

# Summarise fit stats

```{r message=FALSE}
summarised_fit_stats <- 
  i_combined_fit_stats %>%
  f_fitted_summary_tables(groups_by=DIM_thresh)
 
  
summarised_fit_stats
```

## Format

```{r message=FALSE}
fit_stats_formatted <- 
  summarised_fit_stats %>% 
  mutate(DIM_thresh = factor(DIM_thresh, 
                             levels = as.character(c(30, 60, 90, 120, 150, 200, 250, 300)))) %>% 
  
  select(DIM_thresh, starts_with(c("R2","MAE", "RMSPE", "CCC","r_","Cb", "DW"))) %>% 
  f_format_pub(DIM_thresh) %>% 
  mutate(across(where(is.double),~signif(.x,3)))

fit_stats_formatted
```

# Plots

## function Plot some individual plots

```{r}

f_plot_sectional <- function(IDs, plot_title = "Title", plot_table = FALSE){
    
  mean_params_ind <- 
    i_combined_params %>% 
    filter(ID %in% IDs) %>% 
    mutate(DIM_thresh = factor(DIM_thresh, 
                               levels = as.character(c(30, 60, 90, 120, 150, 200, 250, 300)))) 
    
  
  p <- i_fitted_MY_all %>%
    filter(ID %in% IDs) %>% 
    left_join(mean_params_ind , by = c('ID','DIM_thresh')) %>% 
      mutate(fitted_MY =  dijkstra_eq(a,b,b0,c,DIM)) %>% 
      select(-a,-b,-b0,-c) %>% 
     mutate(ID = factor(ID, ordered=TRUE,  levels = as_factor(IDs))) %>% 
    filter(fitted_MY <= 70) %>% 
    group_by(ID) %>% 
    ggplot()+
    geom_point(aes(x=DIM, y=my))+
    geom_line(aes(x=DIM, y=fitted_MY, colour = DIM_thresh), linewidth = 1)+
    scale_x_continuous(n.breaks = 15)+ 
    labs(title = plot_title)+
    ggpubr::theme_classic2()+
    viridis::scale_colour_viridis(discrete = TRUE, option = "H", begin=0.15, end=0.85)+
    geom_vline(aes(xintercept=305), colour='red',linetype = 'dashed')+
    geom_label(aes(x = 305, y = 55, label = '305 DIM'), 
             colour = 'red', label.size = 0.8, size = 9/.pt, 
             data = ~slice_head(.x, n=1))+
    facet_wrap(facets = "ID", ncol=2, scales = "free")+
    scale_y_continuous(limits = c(0,70), n.breaks = 10)+
    ylab("Milk Yield (kg/d)")+
    xlab("Days in milk (DIM)")+
    labs(colour = 'DIM Threshold')
  
  if(plot_table){
    table_to_plot <- 
      mean_params_ind %>% 
      mutate(ID = factor(ID, ordered=TRUE,  levels = as_factor(IDs))) %>% 
      select(ID,DIM_thresh, a, b, b0, c) %>% 
      mutate(across(where(is.numeric), ~round(.x,3))) %>% 
      mutate(across(a, ~round(.x,1))) %>%  
      group_by(ID) %>%
      nest() %>%  #nest table to col called data to plot within each facet using geom_table
      mutate(x = 4, y = 110)
    
    p <- p +
      scale_y_continuous(limits = c(0,110), n.breaks = 11)+
     geom_table(aes(x = x, y = y, label = data), data = table_to_plot,size = 2)+
      NULL
      
  } 
  
  return(p)
  
}
```

### Example bad plots

Plot worst fits from 30 DIM for lacs over 400 DIM

```{r}
# filter out some IDs to plot
longer_lacs <- 
  i_fitted_MY_all %>% 
  group_by(ID) %>% 
  mutate(maxDIM = max(DIM)) %>% 
  filter(DIM_thresh == 30 & maxDIM >= 400) %>% pull(ID) %>% unique()


worst_fits2 <- i_combined_fit_stats %>% filter(ID %in% longer_lacs & DIM_thresh %in% c(30) ) %>% group_by(DIM_thresh) %>% slice_max(order_by = MAE, n = 4)

worst_fits_ID2 <- worst_fits2 %>% pull(ID) %>% unique()
```

```{r fig.width=10}
p_example_problems <- 
  f_plot_sectional(
    worst_fits_ID2,
    plot_title = ifelse(is_constrained, "b)", "a)"), 
    plot_table = TRUE) 

p_example_problems
```


# Mean Fitted Plot

```{r fig.width = 8}
mean_fits_per_threshold <-
  i_fitted_MY_all %>% 
  group_by(DIM_thresh, DIM) %>%
  summarise(mean_predicted_my = mean(fitted_MY),
            sd_predicted_my = sd(fitted_MY),
            mean_observed_my = mean(my, na.rm=TRUE))

p_mean_fitted_sectional <- 
  mean_fits_per_threshold %>% 
  ggplot()+
  geom_point(aes(x=DIM, y = mean_observed_my, colour = 'observed' ), alpha=0.2, size = 1.5)+
  geom_point(aes(x = DIM, y = mean_predicted_my, colour = DIM_thresh), size=1.5, alpha=0.7)+
  ggpubr::theme_classic2()+
  scale_colour_manual( values = c(viridis::turbo(8, begin = 0.15, end = 0.85), "#000000"), #use viridis colours + black at end
                       breaks = c(30,60,90,120,150,200, 250, 300,'observed'))+ # re-order legend
  scale_y_continuous(n.breaks = 10, limits = c(NA,60)) + 
  scale_x_continuous(breaks = c(0,30,60,90,120,150,200, 250, 300), 
                     limits = c(NA, 320)
                     )+
  geom_vline(aes(xintercept=305), colour = 'red', linetype = 'dashed', linewidth=1.2)+
  geom_label(aes(x = 305, y = 50, label = '305 DIM', fontface = 'bold'), 
             colour = 'red', label.size = 1, size = 14/.pt, 
             data = ~head(.x, 1))+ 
  ylab("Milk Yield (kg)")+
  xlab("Days in milk (DIM)")+
  labs(colour = 'DIM Threshold')+
  theme(text = element_text(size=16))+
  ggtitle(ifelse(is_constrained, "b)", "a)"))


p_mean_fitted_sectional  
```

```{r eval = FALSE}
ggsave(filename = paste0(
  ifelse(is_constrained, "CONSTRAINED_", "DEFAULT_"),
  "fitted_sectional_fits_", 
  format(Sys.time(), "%Y%m%d_%H%M") ,
  ".png"),
  path = "./Outputs/Forecasts/",
  plot = p_mean_fitted_sectional,
  dpi = 300,
  width=10,
  height=5)


# Save as RDS to allow re-importing ggplot to combine the constrained and default later for publication
saveRDS(
  p_mean_fitted_sectional,
  file = paste0("./Outputs/Forecasts/",
                ifelse(is_constrained, "CONSTRAINED_", "DEFAULT_"),
                "fitted_sectional_fits_", 
                format(Sys.time(), "%Y%m%d_%H%M") ,
                ".rds")
  )
```

# Forecasted 305 d Model Error
Calculate MY at d 305 MY goodness-of-fit
```{r}
MY_305d_GOF <-  
  i_fitted_305d_MY %>% 
  mutate(DIM_thresh = factor(DIM_thresh, 
                             levels = as.character(c(30, 60, 90, 120, 150, 200, 250, 300)))) %>% 
  group_by(DIM_thresh) %>% 
  summarise(temp = f_goodness_of_fit(mean_305d_MY,mean_fitted_305d_MY, n_params = 4) ) %>% 
  unnest(temp) %>% 
  mutate(log10_RMSPE = log10(RMSPE),
         across(where(is.numeric), ~signif(.x,3))) 
  

MY_305d_GOF
```

## Format

```{r}
MY_305d_GOF_formatted <-
  MY_305d_GOF %>% 
  select(DIM_thresh, RMSPE, MAE, CCC, Cb, r) %>% 
  pivot_longer(cols = where(is.double)) %>% 
  arrange(DIM_thresh) %>% 
  pivot_wider(names_from = DIM_thresh, values_from=value)

MY_305d_GOF_formatted
```

# Violin plot - 305d MY predictions

```{r}

# get actual values to row bind to df for plotting, so that it can be on same x axis easily
df_actual_305d <- 
  i_fitted_305d_MY %>% 
  filter(DIM_thresh == "30") %>% #need just 1 set of this long data
  mutate(DIM_thresh = "observed",
         mean_fitted_305d_MY = mean_305d_MY) 


violin_305d <- 
  i_fitted_305d_MY %>% 
  bind_rows(df_actual_305d) %>% 
  mutate(pred_vs_actual = case_when(DIM_thresh == 'observed' ~ 'observed', TRUE ~ 'predicted')) %>% 
  mutate(DIM_thresh = factor(DIM_thresh, 
                             levels = as.character(c(30, 60, 90, 120, 150, 200, 250, 300, 'observed')))) %>% 
  ggplot(aes(x = DIM_thresh, y = mean_fitted_305d_MY, color = pred_vs_actual))+
  geom_violin(size = 0.7)+
  geom_jitter(width = 0.2, alpha=0.25)+
  viridis::scale_colour_viridis(discrete = TRUE, option = "H", begin = 0.15, end = 0.85)+
  scale_y_continuous(breaks = seq(0,110,10))+
  coord_cartesian(ylim = c(0,110))+
  ggpubr::theme_classic2()+
  theme(legend.position = 'none',
        text = element_text(size=16))+
  labs(x = 'DIM Threshold', y = 'Milk Yield at d 305 (kg)',
       title = ifelse(is_constrained, "b)", "a)"))


violin_305d
```

```{r}
violin_plot_out_of_bounds <- 
  i_fitted_305d_MY %>% 
  filter(mean_fitted_305d_MY > 110) %>% 
  ungroup() %>% 
  summarise(
    n = n(),
    min = min(mean_fitted_305d_MY),
    max = max(mean_fitted_305d_MY)
  ) %>% 
  mutate(is_constrained = is_constrained)

violin_plot_out_of_bounds
```

```{r eval = FALSE}
ggsave(filename = paste0(
  ifelse(is_constrained, "CONSTRAINED_", "DEFAULT_"),
  "violin_plot_305d_sectional_", 
  format(Sys.time(), "%Y%m%d_%H%M") ,
  ".png"),
  path = "./Outputs/Forecasts/",
  plot = violin_305d,
  dpi = 300,
  width=9,
  height=5)


# Save as RDS to allow re-importing ggplot to combine the constrained and default later for publication
saveRDS(
  violin_305d,
  file = paste0("./Outputs/Forecasts/",
                ifelse(is_constrained, "CONSTRAINED_", "DEFAULT_"),
                "violin_plot_305d_sectional_", 
                format(Sys.time(), "%Y%m%d_%H%M") ,
                ".rds")
  )
```

Count 0's in low DIM sectional fits:

```{r}
n_0kg_305d <- 
i_fitted_305d_MY %>% 
  mutate(DIM_thresh = factor(DIM_thresh, 
                             levels = as.character(c(30, 60, 90, 120, 150, 200, 250, 300)))) %>% 
  mutate(pred_is_0 = case_when(mean_fitted_305d_MY <1 ~ TRUE,
                               TRUE ~ FALSE)) %>% 
  group_by(DIM_thresh, pred_is_0) %>% 
  count() %>% 
  group_by(DIM_thresh) %>% 
  mutate(n_perc = round(n/sum(n)*100,0)) 

n_0kg_305d
  
```


# P values

## summary

```{r}
# with SE
P_summary_with_SD <-
  P_values_wide %>% 
  group_by(DIM_thresh) %>% 
  summarise(across(where(is.double), 
                   list(mean= ~mean(.x, na.rm=TRUE),SD=~sd(.x, na.rm=TRUE)), 
                   .names = '{.col}_{.fn}')) %>% 
  mutate(across(contains('mean'), ~signif(.x,2)),
         across(contains("SD"), ~signif(.x,3)))

P_summary_with_SD
```


## Thresholds and accuracy

Example of how accuracy is classified:

| X_305 (threshold) | Observed MY | P \>= 0.5 | Obs \>= X_305 | is correct? |
|-------------------|-------------|-----------|---------------|-------------|
| 15                | 16          | TRUE      | TRUE          | correct     |
| 15                | 16          | FALSE     | TRUE          | incorrect   |
| 15                | 14          | TRUE      | FALSE         | incorrect   |
| 15                | 14          | FALSE     | FALSE         | correct     |

Therefore, accuracy =  number of rows where correct / total number of rows (364) * 100
[for each threshold and probability ]

```{r}
P_values_classified <- 
P_values_full %>% 
  filter(X_305 %in% c(15,20,25) & DIM_thresh %in% c(90,120,200,300)) %>% 
  select(-RMSPE_adj, -n,-t_stat) %>% 
  ungroup() %>% 
  mutate(observed_GE_target = mean_305d_MY >= X_305,
         P_G_0.5 = P > 0.5,
         accur_0.5 = observed_GE_target == P_G_0.5,
         P_G_0.75 = P > 0.75,
         accur_0.75 = observed_GE_target == P_G_0.75,
         P_G_0.95 = P > 0.95,
         accur_0.95 = observed_GE_target == P_G_0.95) 


P_summarised_accuracy <- 
  P_values_classified %>% 
  group_by(DIM_thresh, X_305) %>% 
  summarise(across(where(is.logical), sum), #sum on logical = count(TRUE)
            n=n()) %>% 
  mutate(
    across(starts_with(c('accur_','P_G_','observed_GE_target')), ~ .x / n *100, .names = '{.col}_perc'),
       ) %>% 
  select(DIM_thresh, X_305, contains('observed_GE_target'), n, contains('0.5'), contains('0.75'), contains('0.95'))

# format with numbers for obsered/probability rows
P_summarised_accuracy_long_perc <- 
  P_summarised_accuracy %>% 
  select(DIM_thresh, X_305, contains('_perc')) %>%
  pivot_longer(cols = observed_GE_target_perc:last_col()) %>% 
  ### sort columsn to match output desired:
  mutate(
    sort_col = case_when(str_detect(name, "observed") ~ 0,
                         str_detect(name, "accur") ~ str_split(name, "_", simplify=TRUE)[,2] %>% as.numeric(),
                         str_detect(name, "P_G") ~ str_split(name, "_", simplify=TRUE)[,3] %>% as.numeric()-0.05)
  ) %>% 
  arrange(DIM_thresh, X_305, sort_col) %>% 
  select(-sort_col) %>% 
  # pivot wider:
  pivot_wider(names_from = DIM_thresh,
              values_from = value) %>% 
  mutate(across(where(is.double), ~signif(.x,3))) 
  
# format all as percentages
P_summarised_accuracy_long <- 
  P_summarised_accuracy %>% 
  select(-n, -accur_0.5, -accur_0.75, -accur_0.95, - P_G_0.5_perc, -P_G_0.75_perc,  P_G_0.95_perc, -observed_GE_target_perc) %>% 
  pivot_longer(cols = observed_GE_target:last_col()) %>% 
  pivot_wider(names_from = DIM_thresh,
              values_from = value) %>% 
  mutate(across(where(is.double), ~signif(.x,3))) 

P_summarised_accuracy_long_perc 
P_summarised_accuracy_long
  

```


# Output tables

```{r}
tables_out_list <- 
  list(
    params_raw = summarised_params,
    params_formatted = summarised_params_formatted,
    fit_stats_raw = summarised_fit_stats,
    fit_stats_formatted = fit_stats_formatted,
    GOF_305d_all = MY_305d_GOF,
    GOF_305d_formatted = MY_305d_GOF_formatted,
    n_0kg_305d = n_0kg_305d,
    P_summary_with_SD = P_summary_with_SD,
    P_raw_classified = P_values_classified,
    P_thresh_summarised = P_summarised_accuracy,
    P_thresh_formatted = P_summarised_accuracy_long,
    P_thresh_formatted_perc = P_summarised_accuracy_long_perc,
    violin_plot_out_of_bounds = violin_plot_out_of_bounds
     )

# export
openxlsx::write.xlsx(tables_out_list,
                     file = paste0(
                       ifelse(is_constrained,
                              "./Outputs/CONSTRAINED_iterated_model_summary_tables ",
                              "./Outputs/DEFAULT_iterated_model_summary_tables "),
                                   format(Sys.time(), "%Y%m%d_%H%M") ,
                                   ".xlsx"),
                     colWidths = "auto")

# round all numbers to 2 significant figures
# tables_out_list2 <-
#   tables_out_list %>%
#   map(~.x %>% mutate(across(where(is.numeric), ~signif(.x, 2))))

```
